\section{Game Play}
The game takes place over a sequence of rounds.
During each round:
\begin{enumerate}
	\item The pilot must reveal the next challenge card. 
	\item The pilot may step down. If two or more players agree to do so, they may spend a recall card to force the pilot to step down.
	\item If the pilot stepped down, then the players must elect a new pilot.
	\item The pilot must play an action card. 
\end{enumerate}
The game ends when any player plays their last action card or after Bobby faces the last challenge.

\subsection{Electing a Pilot}
Each player must vote for an aspect by turning their corresponding voting card face up.
The aspect who receives the most votes wins the election. 

In the case of a tie, the Student must decide which of the leading vote-getters wins the election. 

The winner of the election must become the new pilot.

\subsection{Playing an Action Card}
The pilot must add one action card to the tableau.
If the rank of the pilot's card meets or exceeds the rank of the challenge card, then Bobby succeeds. Otherwise, Bobby fails.

The pilot's card is added to the tableau in the row corresponding to the suit of the challenge card. If Bobby succeeds, then the pilot's card is played face up.  Otherwise, their card is played face down. 

\subsection{Scoring}
The score for each player is given by:
\begin{playerlistnarrow}
	\item[The Animal\normalfont{:}] total physical successes.
	\item[The Angel\normalfont{:}] total social successes.
	\item[The Genius\normalfont{:}] total mental successes.
	\item[The Student\normalfont{:}] total failures.
\end{playerlistnarrow}
The players with the highest scores win the game.
\newpage

