\section{The Tableau}
The tableau represents Bobby's long-term memory.
Each time Bobby faces a challenge, the pilot will add an action card to the tableau.
The tableau consists of three rows of cards, one for each type of challenge.

At the beginning of the game, the tableau is empty. A label card is used to indicate the position of the start of each row as in the following diagram:

\begin{figure}[h]\centering
\begin{tikzpicture}[scale=0.9]
	\pic[rotate=90, transform shape] () at (0,32mm) {clubscard={\ace}};
	\pic () at (15mm, 32mm) {dottedcardoutline};
	\pic () at (27mm, 32mm) {dottedcardoutline};
	\pic () at (39mm, 32mm) {dottedcardoutline};
	\pic () at (51mm, 32mm) {dottedcardoutline};
	\node[draw, fill=black, circle, inner sep=0.5pt] () at (59mm,32mm) {};
	\node[draw, fill=black, circle, inner sep=0.5pt] () at (61mm,32mm) {};
	\node[draw, fill=black, circle, inner sep=0.5pt] () at (63mm,32mm) {};

	\pic[rotate=90, transform shape] () at (0,16mm) {heartscard={\redace}};
	\pic () at (15mm, 16mm) {dottedcardoutline};
	\pic () at (27mm, 16mm) {dottedcardoutline};
	\pic () at (39mm, 16mm) {dottedcardoutline};
	\pic () at (51mm, 16mm) {dottedcardoutline};
	\node[draw, fill=black, circle, inner sep=0.5pt] () at (59mm,16mm) {};
	\node[draw, fill=black, circle, inner sep=0.5pt] () at (61mm,16mm) {};
	\node[draw, fill=black, circle, inner sep=0.5pt] () at (63mm,16mm) {};

	\pic[rotate=90, transform shape] () at (0,0) {spadescard={\ace}};
	\pic () at (15mm, 0) {dottedcardoutline};
	\pic () at (27mm, 0) {dottedcardoutline};
	\pic () at (39mm, 0) {dottedcardoutline};
	\pic () at (51mm, 0) {dottedcardoutline};
	\node[draw, fill=black, circle, inner sep=0.5pt] () at (59mm,0) {};
	\node[draw, fill=black, circle, inner sep=0.5pt] () at (61mm,0) {};
	\node[draw, fill=black, circle, inner sep=0.5pt] () at (63mm,0) {};
\end{tikzpicture}
\caption*{An empty tableau.}
\end{figure}

\bigskip
At the end of the game, the state of the tableau will be used to compute the players' scores.

\section{Set Up}
To prepare to play the game the players should:
\begin{enumerate}
\item Place the label cards face up in the middle of the play area to indicate the location of the tableau.
\item Shuffle the challenge cards and place them face down near the tableau.
\item Deal an aspect card to each player. The players should place their aspect cards face up in the play area in front of themselves.
\item Collect all of the voting cards of the same suit as their aspect cards. The players should place their voting cards face down near their aspect card.
\item Collect all of the action cards of the same suit as their aspect cards.
\item Place the recall cards face up near the tableau. 
\end{enumerate}
The Student is the starting pilot.

