\section{Variants}
There are several variants of the basic game that experienced players may want to explore. These variants add some additional complexity to the game and allow for more strategic play.

\subsection{Multi-game Sessions}
The players can agree to play several games in a single session and combine their scores in the individual games to compute a single overall \emph{session score}.

Each player's session score is the sum of the player's scores in the individual games. The players with the highest session scores win.

Alternatively, the players can agree to play until one player's session score exceeds some threshold. A reasonable choice for the threshold is twenty points.
	
\subsection{Aspect Affinities} 
The players can agree to allow players to add two cards to the tableau when the suit of the challenge card matches that of the pilot.

If the sum of the ranks of the two cards meets or exceeds the rank of the challenge card, then Bobby succeeds. Otherwise, Bobby fails.

\vfill

\section{Acknowledgements}
The design of Head Trip has been vastly improved by the influence of ideas and mechanics from other games and the feedback provided by playtesters throughout the design process.

The following tools were used to create this leaflet:
\begin{description}[labelindent = 0.25cm, itemsep=0pt, leftmargin=0.25cm]
	\item[Typesetting\normalfont{:}] XeLaTeX.
	\item[Diagrams\normalfont{:}] TikZ, GIMP.
	\item[Fonts\normalfont{:}] Libre Clarendon, Charter, Card~Characters.
\end{description}

\medskip

\textbf{Contact}: \href{mailto:head.trip.card.game@gmail.com}{head.trip.card.game@gmail.com}

\smallskip

\begin{tabular}{@{}m{\textwidth-\widthof{\Huge{\doclicenseIcon}}}@{}m{\widthof{\Huge{\doclicenseIcon}}}@{}}
\footnotesize{This work is licensed under a Creative Commons\newline ``Attribute 4.0 International'' license.} & \Huge{\doclicenseIcon} \\
\end{tabular}
