\subsection{Challenge Cards}
Each challenge card represents a challenge that Bobby faces during the game. Every challenge has both a type and a difficulty.

The type of a challenge represents the skills that Bobby will need to employ to successfully face that challenge. There are three types of challenge, each of which requires different skills:
\begin{challengetypelist}[itemsep=0pt]
	\item[\clubs\ (Physical):] requires athleticism or aggression. 
	\item[\hearts\ (Social):] requires empathy or insight.
	\item[\spades\ (Mental):] requires creativity or analysis.
\end{challengetypelist}

The difficulty of a challenge is represented by the rank of its challenge card. The higher the rank, the more difficult the challenge.

When Bobby faces a challenge, the pilot will play an action card. Bobby succeeds if the rank of that action card meets or exceeds that of the challenge card.

\subsection{Location Cards}

Each location card represents a place where Bobby might be found on a school day. With the exception of Bobby's House (where the story might begin or end) and the School Bus, all of these locations are different rooms in Bobby's school. 
\vspace{-1.75ex}
\begin{multicols}{2}
\begin{cardlist}[itemsep=0pt, topsep=0pt, partopsep=0pt]
  \item[\redtwo\diamonds:] Bobby's House
  \item[\redthree\diamonds:] School Bus
  \item[\redfour\diamonds:] Classroom
  \item[\redfive\diamonds:] Cafeteria
  \item[\redsix\diamonds:] Principal's Office
  \item[\redseven\diamonds:] Hallway
  \item[\redeight\diamonds:] Library
  \item[\rednine\diamonds:] Auditorium
  \item[\redten\diamonds:] Locker Room
  \item[]
\end{cardlist}
\end{multicols}

\subsection{Character Cards}
Each character card represents a person that Bobby might encounter at school. These include other kids, family members, school faculty, and other adults.
\vspace{-1.75ex}
\begin{multicols}{2}
\begin{cardlist}[itemsep=0pt, topsep=0pt, partopsep=0pt]
  \item[\redjack\diamonds:] Bully
  \item[\redqueen\diamonds:] Crush
  \item[\redking\diamonds:] Friend
  \item[\queen\clubs:] Neighbour
  \item[\king\clubs:] Janitor
  \item[\jack\spades:] Principal
  \item[\queen\spades:] Teacher
  \item[\redjack\hearts:] Sibling
  \item[\redking\hearts:] Parent
  \item[\hspace{0.19cm}\joker:] Stranger
\end{cardlist}
\end{multicols}
