\section{Overview}
Head Trip, as described in the Player's Guide, is a competitive card game for four players.
In that version of the game, each player portrays one aspect of the personality of a teenage boy named Bobby.
These aspects compete with one another to control Bobby's actions as he faces a series of challenges.

The Headmaster's Guide describes an additional role for an additional player, the \emph{Headmaster}.
Rather than portraying an aspect of Bobby's personality, the Headmaster's job is to provide narrative context for everything that happens during the game.

This transforms Head Trip into a semi-cooperative roleplaying game in which the Headmaster helps the other players tell a story about Bobby's experiences.

These rules assume that the reader is familiar with the game described in the Player's Guide.

\section{The Cards}
In this version of the game, the players will use the \emph{Headmaster's deck} instead of the auxiliary deck described in the Player's Guide.
The Headmaster's deck is a complete (54-cards) standard deck of playing cards. It consists of:

\begin{auxiliarydecklist}
	\item[Challenge Cards\hfill\normalfont{(27):}] \two\ \textendash\ \ten\ of \clubs, \hearts, \spades.
	\item[Aspect Cards\hfill\normalfont{(4):}] \jack\clubs, \queen[red]\hearts[red], \king\spades, \ace[red]\diamonds[red].
	\item[Label Cards\hfill\normalfont{(3):}] \ace\clubs, \ace[red]\hearts, \ace\spades.
	\item[Location Cards\hfill\normalfont{(9):}] \redtwo\ \textendash\ \redten\ of \diamonds.
	\item[Character Cards\hfill\normalfont{(11):}] remaining \jack, \queen, \king, \joker\ cards.
\end{auxiliarydecklist} 

Notice that the challenge cards, aspect cards, and label cards are the same as those that comprise the auxiliary deck. The setting cards are not used in the game described in the Player's Guide.

So, this version of the game can still be played with two standard decks of playing cards. The Headmaster will use cards from the Headmaster's deck while the other players will use cards from the persona deck. 
