\section{Variants}
Most of the rules of the game are independent of the setting elements. So, it is easy to modify the game to tell different kinds of stories.

\subsection{Other Settings}
Some players may want to explore Bobby's life outside of school. 

If the Headmaster is confident in their ability to improvise then they can simply invent new setting elements on the fly as required.

Otherwise, they can make their own lists of what the various location cards and character cards represent.

\subsection{Other People}
Some players may want to portray the aspects of the personality of someone other than Bobby.

In some cases, for example if the players want to play as aspects of Annie's personality, only names need to be changed and the setting elements can be left as is.

In other cases, the default setting won't make sense for the new person and the Headmaster will have to modify the setting accordingly.

\vfill

\section{Acknowledgements}
The design of Head Trip has been vastly improved by the influence of ideas and mechanics from other games and the feedback provided by playtesters throughout the design process.

The following tools were used to create this leaflet:
\begin{description}[labelindent = 0.25cm, itemsep=0pt, leftmargin=0.25cm]
	\item[Typesetting\normalfont{:}] XeLaTeX.
	\item[Diagrams\normalfont{:}] TikZ, GIMP.
	\item[Fonts\normalfont{:}] Libre Clarendon, Charter, Card~Characters.
\end{description}

\medskip

\textbf{Contact}: \href{mailto:head.trip.card.game@gmail.com}{head.trip.card.game@gmail.com}

\smallskip

\begin{tabular}{@{}m{\textwidth-\widthof{\Huge{\doclicenseIcon}}}@{}m{\widthof{\Huge{\doclicenseIcon}}}@{}}
\footnotesize{This work is licensed under a Creative Commons\newline ``Attribute 4.0 International'' license.} & \Huge{\doclicenseIcon} \\
\end{tabular}
